Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-23 paper/paper.tex
Rewritten old discussion of results section

\subsection{Experimental Parameters}

\TODO{Edit this first paragraph, which was moved from the old Scenarios section}

@@

\begin{figure*}[htb] 
\TODO{Cut this figure down}\\
\centering
\includegraphics[width=0.19\textwidth]{pareto-cost-MONTAGE-n-1000-8-dagh1-20m0}
\includegraphics[width=0.19\textwidth]{pareto-cost-CYBERSHAKE-n-1000-8-dagh1-20m0}
\includegraphics[width=0.19\textwidth]{pareto-cost-LIGO-n-1000-8-dagh1-40m0}
\includegraphics[width=0.19\textwidth]{pareto-cost-GENOME-n-1000-8-dagh100-1500m0}
\includegraphics[width=0.19\textwidth]{pareto-cost-SIPHT-n-1000-8-dagh5-50m0}
\caption{Effective computing cost in \$ per hour calculated by dividing the sum of
task runtimes by the total budget. Higher costs result from lower resource utilization. Data based on DPDS, AW-DPDS and SPSS algorithms for ensembles of 100
Pareto-distributed workflows. The ranges on $y$ axis are chosen to 
emphasize the differences  between  the performance of the algorithms.}
\label{fig:cost}
\end{figure*}

\TODO{Rewrite this next paragraph}

These observations are further confirmed when examining the effective computing
cost, as shown in Figure~\ref{fig:cost}. It can be seen that lower resource
utilization and lower parallel efficiency for short deadlines lead to
substantial increases in the effective computing cost. This increase can be 
significant. For example, a SIPHT ensemble with short deadlines and a budget
of \$1,000 has an effective computing cost $\sim$8--20\% higher than the 
minimum effective cost of \$1/hour, depending on the algorithm used. This means 
that out of the \$1,000 budget, \$80--\$200 is spent on idle resources.

Another general conclusion can be drawn from Figure~\ref{fig:cost}: despite some
random fluctuations resulting mostly from the finite result space, all the
curves for all the applications and budgets have a similar shape. This shape
represents a trade-off curve between two conflicting objectives: time and cost.
We observe that the selection of deadline and cost can be formulated as a
multi-criteria optimization problem, and that the curves presented in 
Figure~\ref{fig:cost} are approximations of the Pareto front (or Pareto set) of
solutions to this problem. In our case the solutions were achieved by maximizing
the amount of work done, which is the inverse of minimizing the effective 
computing cost metric for a given deadline. Therefore, the obtained results 
can be used to aid in resource allocation planning, when both cost and time 
criteria are given not as constraints but as objectives.

\begin{figure}[htb]
    \TODO{Does this figure need removed?}
    \centering
    \subfloat[size]{
        \includegraphics[width=0.75\columnwidth]{size-selected-LIGO}
        }\\
    \subfloat[cost]{
        \includegraphics[width=0.75\columnwidth]{cost-selectedLIGO}
        }
    \caption{Example performance of algorithms expressed in
    sum of dag sizes and effective cost, data for LIGO application, Pareto
    Sorted ensemble of 100 workflows.}
    \label{fig:size-cost}
\end{figure}

>>>>

\subsection{Experimental Parameters}
\label{sec:exp-parameters}
\TODO{Edit this first paragraph, which was moved from the old Scenarios section}

@@

% New rewritten text for section ``discussion of Results'' starts here

\begin{figure}[htb]
    \centering
    \subfloat[size]{
        \includegraphics[width=0.75\columnwidth]{size-selected-LIGO}
        }\\
    \subfloat[cost]{
        \includegraphics[width=0.75\columnwidth]{cost-selectedLIGO}
        }
    \caption{Example performance of algorithms expressed in
    sum of dag sizes and effective cost, data for LIGO application, Pareto
    Sorted ensemble of 100 workflows.}
    \label{fig:size-cost}
\end{figure}

To analyze the behaviour of algorithms we ran simulations for constraint values
ranging between the estimated limits indicated in Section~\ref{sec:exp-parameters},
resulting in $10 * 10 = 100$ (budget, deadline) data points for each of 5 applications, 3 algorithms and
using 5 ensemble size distributions and 10 random seeds. From this result space
of 75000 we selected representative plots.

Fig.~\ref{fig:size-cost}a shows example of a performance curve using the total computing
time metric, $T_C$ for LIGO application with pareto Sorted distribution of
workflows. It can be seen that SPSS gives the best performance and WA-DPDS
performs better than the workflow-unaware version, DPDS. 
This means that for the workflows we tested the simple admission procedure based 
on estimation of workflow cost does not degrade the solution, but rather in 
many cases it enables larger workflows that would lead to budget overrun to
be rejected. Thus it can save the space for smaller workflows to complete.

This plot allows us observe a more general property: for a given budget,
when the deadline is tightened the amount of work done steeply decreases. 
This is partially due to the fact that fewer workflows can be
completed given a short deadline because their critical paths are simply too long
and they are squeezed out of early start times by high priority workflows.
In addition, assigning a shorter deadline means that more VMs need to be
provisioned to complete the work. However, because of the dependencies in the 
workflows, many of these VMs will either be idle, or will be backfilled with 
tasks from low-priority workflows that never finish, resulting, effectively, 
in reduced resource utilization and fewer completed workflows.

These observations are further confirmed when examining the effective computing
cost, as shown in Figure~\ref{fig:size-cost}b. It can be seen that lower
resource utilization and lower parallel efficiency for short deadlines lead to
substantial increases in the effective computing cost. This increase can be 
significant. For example, for short deadlines an effective computing cost
is $\sim$10--40\% higher than the minimum effective cost of \$1/hour, depending
on the algorithm used. This means that out of the \$1,000 budget, \$100--\$400
is spent on idle resources.

Another general conclusion can be drawn from Figure~\ref{fig:size-cost}b:
all the curves for all the applications and budgets have a similar shape. This
shape represents a trade-off curve between two conflicting objectives: time and cost.
We observe that the selection of deadline and cost can be formulated as a
multi-criteria optimization problem, and that the curves presented in 
Figure~\ref{fig:size-cost}b are approximations of the Pareto front (or Pareto
set) of solutions to this problem. In our case the solutions were achieved by maximizing
the amount of work done, which is the inverse of minimizing the effective 
computing cost metric for a given deadline. Therefore, the obtained results 
can be used to aid in multi-criteria resource allocation planning, when both
cost and time criteria are given not as constraints but as objectives.
